RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2016-06-27 manuscripts/manuscript.Rmd

This project was supported in part by the National Evolutionary
Synthesis Center (NESCent) (NSF #EF-0905606), and grants from the
National Science Foundation (DBI-1306697) and the Alfred P Sloan
Foundation (Grant 2013-6-22). `RNeXML` started as a project idea for
the Google Summer of Code(TM), and we thank Kseniia Shumelchyk for taking
the first steps to implement it. We are grateful to F. Michonneau for
helpful comments on an earlier version of this manuscript, and reviews
by Matthew Pennell, Associate Editor Richard FitzJohn, and an anonymous
reviewer. At their behest, the reviews of FitzJohn and Pennell can be found in this
project's GitHub page at [github.com/ropensci/RNeXML/issues/120](https://github.com/ropensci/RNeXML/issues/121) and [github.com/ropensci/RNeXML/issues/120](https://github.com/ropensci/RNeXML/issues/120), together with our replies and a record of our revisions.

>>>>

This project was supported in part by the National Evolutionary
Synthesis Center (NESCent) (NSF #EF-0905606), and grants from the
National Science Foundation (DBI-1306697) and the Alfred P Sloan
Foundation (Grant 2013-6-22). `RNeXML` started as a project idea for
the Google Summer of Code(TM), and we thank Kseniia Shumelchyk for taking
the first steps to implement it. We are grateful to F. Michonneau for
helpful comments on an earlier version of this manuscript, and reviews
by Matthew Pennell, Associate Editor Richard FitzJohn, and an anonymous
reviewer. At their behest, the reviews of FitzJohn and Pennell can be found in this
project's GitHub page at [github.com/ropensci/RNeXML/issues/121](https://github.com/ropensci/RNeXML/issues/121) and [github.com/ropensci/RNeXML/issues/120](https://github.com/ropensci/RNeXML/issues/120), together with our replies and a record of our revisions.
